The title

### 2023-01-17 docs/draft/draft.Rmd
draft comments

** big picture = social implications of online teaching and how that has changed in a post-pandemic world
** small picture = what we are doing in this language program and how can we improve to meet the needs and wants of the students in their new reality

- Address the general idea

- Explain the study

- Address our contribution

@@

# Literature Review

Online learning comes with a new set of challenges that are not found in a traditional classroom setting, especially when, for many, it was not an option to have class anywhere but virtually. 
Being forced to switch modalities had consequences, both from the teachers’ and students’ perspectives, as they were either not ready for the change or lacked many materials. 
Top Hat (2020) did a major survey on undergraduate students’ and teachers’ perceptions during the online emergency switch in US universities. 
Their findings within students taking a language class were that overall, the quality of instruction received was worse in comparison to the in-person learning setting (*insert citation*)
In the same way, a vast majority of students felt that the class experience was unengaging as they missed spending time with faculty and fellow students. 
Within this swift change to online settings, many students also found that their academic load was not only reduced but also experienced problems with using online tools. <!--- i'm going to think about how to reframe this paragraph --->

Language attitudes are key in the language learning environment, as they can determine the success of a student [ eg @thompson2021attitudes]. 
A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged.
Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities [ @alqurashi2016self; @horvat2015student; @ke2013constructs; @lan2010using]. 
Within this framework, anxiety has been linked in several research studies [e.g.,@teimouri2019second] as an indicator of poor linguistic development. 
Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment. 
Furthermore, @webb2014flipping studied the attitudes of students and teachers in a flipped online classroom of Chinese. 
Their results showed an incremental fluctuation in their perception. 
That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term. 
A similar psychological development is observed in @ushida2005role study which investigated the changes in students’ attitudes and motivation over time in online language courses. 
Their results showed a similar evolution within the student’s attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term. 
Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al. 2018), as well as the familiarity and complexity of the instruments that the course requires (@heckel2019pride), which might involve some training and assistance before the beginning of the online course. 
During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, @tomasik2021educational, leading to an overall feeling of less effective education Top hat (2020), @hodges2020difference, @lee2022factors. 
While the immediate transition to online education seemed rushed in @ruiz2022transitioning the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting. 
Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format. 
Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments [@chakraborty2021opinion].

The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years. 
This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education. 
With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes. 
The goal of this paper is dual, first to determine if online education is still in demand among our undergraduate students, and to identify what are the attitudes towards it in a context where online education is no longer mandatory. Our second goal is to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.

# Research gap and theoretical approach

Education mirrors society and its challenges, with Covid-19 as a global example of the adaptations that educators around the world had to implement in order to continue providing education to their students. 
In this sense, education can be understood as a continuum that has endlessly developed according to the socioeconomic changes that society experiences throughout history.

Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. 
The effects of this ever-changing learning environment have affected students and continue to affect the way they interact with and view their education. 
Post-pandemic effects, along with world socio-economic changes such as inflation and the need to work, have brought a new educational reality that affects tendencies toward language enrollment. 
To better understand these tendencies, we employed the lens of The Grounded Theory, as it allows a cyclical observation of a changing world. 
The Grounded Theory considers a changing environment that can evolve, becoming the researcher a constant observer of the changes produced [@hernandez2014investigacion]. 
Having a better understanding of the constant change of tendencies that affect our students can help us not only to provide them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.

This theoretical approach allowed us to perform mixed models including qualitative, quantitative, and open questionary deriving the hypothesis we present in this paper. 
This approach was chosen as it allows the researcher to observe a constant change in tendencies and derive a hypothesis based on the collected data.  
Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within our community of students and the factors that affect them [@corbin2014basics].

@@

Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. 
The effects of this ever-changing learning environment have affected students and continue to affect modulating the way they interact with and view their education. Post-pandemic effects, along with world socio-economic changes, have brought a new educational reality that affects tendencies toward enrollment. 
Having a better understanding of the constant change of tendencies that affect our students can help us not only in providing them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.

>>>>

Language attitudes are key in the language learning environment, as they can determine the success of a student [eg @thompson2021attitudes]. <!--- lets avoid statements that are very direct and assertive like that, something more like "they play a role in determining the success of a student ---> 
A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged (*insert citation*).
Interestingly, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities [@alqurashi2016self; @horvat2015student; @ke2013constructs; @lan2010using]. 
Within this framework <!---i'm not sure that framework is the right word here-->, anxiety has been linked in several research studies [e.g.,@teimouri2019second] as an indicator of poor linguistic development. 
<!--- i think this sentence should be deleted "Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment." --> 
<!--- i'm going to think about how to rework these examples into a paragraph that flows a little better Furthermore, @webb2014flipping studied the attitudes of students and teachers in a flipped online classroom of Chinese. 
Their results showed an incremental fluctuation in their perception. 
That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term. 
A similar psychological development is observed in @ushida2005role study which investigated the changes in students’ attitudes and motivation over time in online language courses. 
Their results showed a similar evolution within the student’s attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term. 
Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al. 2018), as well as the familiarity and complexity of the instruments that the course requires (@heckel2019pride), which might involve some training and assistance before the beginning of the online course. 
During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, @tomasik2021educational, leading to an overall feeling of less effective education Top hat (2020), @hodges2020difference, @lee2022factors. 
While the immediate transition to online education seemed rushed in @ruiz2022transitioning the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting. 
Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format. 
Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments [@chakraborty2021opinion]. --->

The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years. 
<!--- This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education. - maybe delete this ---> 
With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes. <!--- idk if we can say "global decrease" maybe something like "with a push to return to pre-covid practices" ---> 
The goal of this paper is twofold, first to identify attitudes towards online language education it in a context where online education is no longer mandatory and to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.

@@

# Previous literature and theoretical framework

<!--- i don't know if this paragraph is necessary "Education mirrors society and its challenges, with Covid-19 as a global example of the adaptations that educators around the world had to implement in order to continue providing education to their students. 
In this sense, education can be understood as a continuum that has endlessly developed according to the socioeconomic changes that society experiences throughout history." --->

The goal of the current paper is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. 
The effects of this ever-changing learning environment have affected students and continue to affect the way they interact with and view their education. 
Post-pandemic effects, along with world socio-economic changes such as inflation and the need to work, have brought a new educational reality that affects tendencies toward language enrollment.

<!-- i think this is what needs to be worked on, if you have something in the introcution that fits in any of these categories, add it below and we can work it into a few paragraph to motivate the study --->

## Online learning

#### Effectiveness

#### Motivation

#### Perception / attitudes

## Grounded theory

In order to study and understand tendencies in online learning, we turned to Grounded Theory, as it allows for a cyclical observation of a changing world, where the researcher is a constant observer of the changes produced [@hernandez2014investigacion]. 
This theoretical approach allowed us to employ a mixed models questionnaire that included qualitative, quantitative, and open-ended questions aimed at gaining information about the participant's experience, attitudes, and motivations for taking online vs. in-person language classes. 
Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within our community of students and the factors that affect them [@corbin2014basics]. <!--- can you elaborate on this? --->

@@

<!--- i think this is "too personal" we should change it to something like, "the current study aims to explore attitudes towards online instruction at an R1 instution in a post-pandemic reality where learning has been adapted to an online learning environment" o algo asi ...
Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. 
The effects of this ever-changing learning environment have affected students and continue to affect modulating the way they interact with and view their education. Post-pandemic effects, along with world socio-economic changes, have brought a new educational reality that affects tendencies toward enrollment. 
Having a better understanding of the constant change of tendencies that affect our students can help us not only in providing them with adequate tools to succeed but also help us in providing courses that match their needs and expectations. --->
